### 2024-07-15 paper.tex
new version
quickfix

\volume{44}

@@

\yearonfooter{xxxx}

@@

@@

\SetWatermarkText{[Fake]}

@@

@@

\englishTitle{Exploring the dynamics of lightning and its thermal effects: Insights from Data collection and analysis}

@@

\shortHeaderTitle{Exploring the Dynamics of Lightning and its Thermal Effects: Insights from Data ...}

>>>>

\volume{xx}

@@

\publishYear{xxxx}
\nEspecial{xx}

@@

\usepackage[fleqn]{amsmath}

@@

\SetWatermarkText{[Draft]}

@@

\setlength{\mathindent}{0pt}

@@

\englishTitle{Exploring the dynamics of lightning and its thermal effects: Insights from data collection and analysis}

@@

\shortHeaderTitle{Exploring the dynamics of lightning and its thermal effects: Insights from Data ...}
